% Created 2026-03-22 Sun 18:49
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{}
\title{Practicum Test - Example}
\hypersetup{
 pdfauthor={Marcus},
 pdftitle={Practicum Test - Example},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 30.2 (Org mode 9.7.11)}, 
 pdflang={English}}
\begin{document}

\maketitle
\section*{Instructions}
\label{sec:orga852b59}


\begin{itemize}
\item \textbf{Test Duration}: 25 minutes
\item Ensure all function names match the specification exactly.
\item No external resources or AI assistance permitted.
\end{itemize}
\section*{Question 1}
\label{sec:org154b7ea}

\subsection*{WHAT YOU ARE ASKED}
\label{sec:org2e8256b}


\textbf{NOTE}:
\begin{itemize}
\item You are required to write the solutions for the parts of this question in the lisp program file \textbf{\textasciitilde{}/quicklisp/local-projects/5ig/Example/pt/q1.lisp} .
\item You may create helper functions in your program file.
\item To ensure your solution is in the correct folder and passes the test cases shown in the examples below,  type the following expression on the REPL:
\end{itemize}

\begin{verbatim}
(cg:chk-my-solution "~/quicklisp/local-projects/5ig/Example/pt/q1.lisp")
\end{verbatim}

Write a Common Lisp function called DOT-PRODUCT-LIST that takes two lists of numbers of equal length. The function should return a list where each element is the product of the numbers at that position. 

In your implementation, you must write and use a helper function called MULTIPLY-RECORDS that takes two numbers and returns their product. You may implement this as a standalone function or locally using LABELS.

\begin{verbatim}
The expression below

  (DOT-PRODUCT-LIST '(1 2 3) '(4 5 6))

should evaluate to

  (4 10 18)
\end{verbatim}

\begin{verbatim}
The expression below

  (DOT-PRODUCT-LIST NIL NIL)

should evaluate to

  NIL
\end{verbatim}
\section*{Question 2}
\label{sec:orgb30df2a}

\subsection*{WHAT YOU ARE ASKED}
\label{sec:org2737868}


\textbf{NOTE}:
\begin{itemize}
\item You are required to write the solutions for the parts of this question in the lisp program file \textbf{\textasciitilde{}/quicklisp/local-projects/5ig/Example/pt/q2.lisp} .
\item You may create helper functions in your program file.
\item To ensure your solution is in the correct folder and passes the test cases shown in the examples below,  type the following expression on the REPL:
\end{itemize}

\begin{verbatim}
(cg:chk-my-solution "~/quicklisp/local-projects/5ig/Example/pt/q2.lisp")
\end{verbatim}

Write a function SQUARE-EVENS that takes a list of integers and returns a new list containing the squares of only the even numbers in the original list, maintaining their relative order. 

\textbf{Constraint}: You are forbidden from using REVERSE or APPEND. You must build the list in the correct order using recursion or iterative collection.

\begin{verbatim}
The expression below

  (SQUARE-EVENS '(1 2 3 4 5 6))

should evaluate to

  (4 16 36)
\end{verbatim}

\begin{verbatim}
The expression below

  (SQUARE-EVENS '(1 3 5))

should evaluate to

  NIL
\end{verbatim}

\begin{verbatim}
The expression below

  (SQUARE-EVENS NIL)

should evaluate to

  NIL
\end{verbatim}
\end{document}
